Proof nets for first-order additive linear logic

### 2018-04-17 ALL1.tex
discussion on table

\begin{figure}[!t]
\begin{center}
\begin{tabular}{lcccc}
 &	Monomial nets & Expansion trees & Witness nets & Unification nets
\\\hline
   Canonicity & \xmark & \vmark & \vmark & \vmark
\\ Generality & \xmark &\xmark&\xmark& \vmark
\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
\\ Coalescence & ? & ? & \vmark & \vmark
\\ Slicing &\vmark &\xmark& \vmark &\xmark
\end{tabular}  
  \caption{Comparison of different notions of proof nets for quantifiers and additive connectives}
  \label{fig:results}
\end{center}
\end{figure}

@@

%\subsection{Alternative approaches: monomial nets and expansion trees}
We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
%
Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}. These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
%
However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to canonicity for first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
%
But the details of this relation are clearly beyond the scope of our paper.

@@

However, for our definition of proof nets, we did not pursue this direction, and consider the choices made in this paper preferable. Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees. More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
%
%%Finally, available space does not permit a detailed exposition, which we defer to a journal version.
%
%We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
%
The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section.

>>>>

\begin{figure}[!t]
\begin{center}
\begin{tabular}{lcccc}
 &	Monomial nets & Expansion trees$^\ast$ & Witness nets & Unification nets
\\\hline
   Canonicity & \xmark & \vmark^\ast & \vmark & \vmark
\\ Generality & \xmark &\xmark&\xmark& \vmark
\\ Direct composition &(\vmark) &\xmark& \vmark & \vmark
\\ Coalescence & ? & ? & \vmark & \vmark
\\ Slicing &\vmark &\vmark^\ast& \vmark & ?
\end{tabular}  
  \caption{Comparison of different notions of proof nets for quantifiers and additive connectives}
  \label{fig:results}
\end{center}
\end{figure}

@@

%\subsection{Alternative approaches: monomial nets and expansion trees}
We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
%
Proof nets with additives and quantifiers existed before as \emph{monomial nets} \cite{Girard-1996}, where slices are managed explicitly with \emph{monomial weights}. These nets are not generally canonical: they admit the permutation (and duplication) of proof rules past implicit \emph{contractions}.
%
However, we do conjecture that additive monomial nets could be restricted to some notion of canonical form, which would be equivalent to the notion induced by \emph{expansion tree proofs}, provide another approach to first-order quantification for classical logic \cite{Miller-1987,Heijltjes-2010}.
%
But the details of this relation are clearly beyond the scope of our paper.

@@

However, for our definition of proof nets, we did not pursue this direction, and consider the choices made in this paper preferable. Witness nets and unification nets retain the original structure of \emph{formulas + links}, without requiring expansion trees. More importantly, as in the propositional case, they enable direct (non-inductive) composition by a relational composition of links.
%
%%Finally, available space does not permit a detailed exposition, which we defer to a journal version.
%
%We have presented two notions of first-order additive proof net, witness nets and unification nets, to canonically capture the two natural notions of proof identity for first-order additive linear logic.
%
The table in Figure~\ref{fig:results} summarizes the results of our paper and the observations in this section, where the column on expansion trees is speculative since they only exist for classical logic, and not (yet) exist for $\all$.
